Updates on the Exoplanet Orbit Database

### 2014-01-24 draft/ms.tex

@@

We only report new additions and revised fields here. For details on
other fields, see \cite{Wright2011}. We divide the fields into
categories in consistency with the interactive table on
exoplanets.org. Some fields are not explicitly included in the
interactive table (e.g., the URLs), but are explicitly listed in the
downloadable {\tt .csv} file.\footnote{The entire dataset provided by
  exoplanets.org is available for download in a single CSV file at
  \url{http://exoplanets.org/csv-files/exoplanets.csv}}

@@

MASSS

@@

@@

We now report uncertainties for a certain field X as XUPPER, XLOWER
and UX. XUPPER and XLOWER store the upper and lower ZZZ 1$\sigma$ ZZZ
uncertainties, and they are different when the error bars are
asymmetric. UX contains the ZZZ 1$\sigma$ ZZZ uncertainty, and it
equals to $({\rm XUPPER+XLOWER})/2$ in the case of asymmetric error
bars. Fields that have XUPPER, XLOWER and UX are: (list of fields).

@@

Added field: ZZZ MONTH ZZZ, PLANETDISCMETH, STARDISCMETH.

@@

@@

S - changed to SHK; What's the source for SHK and RHK? Still discovery
paper and Butler 2006?

@@

I\dotfill & Float & Orbital inclination in degrees (ZZZ for transiting
systems only) & -UPPER, etc. \\

@@

SET\dotfill & & ZZZ Epoch of secondary eclipse center in

@@

ZZZ MONTH ZZZ\dotfill & Integer & Month of publication of FIRSTREF & \nodata \\

@@

\tablenotetext{d}{ZZZ Is this now consistent? ZZZ}

>>>>

According to Google Analytics, $47,000$ people visited exoplanets.org
in 2013.

@@

We only describe new additions and revised fields here, but list all
fields. For details on other fields, see \cite{Wright2011}. We divide
the fields into categories in consistency with the interactive table
on exoplanets.org. Some fields are not explicitly included in the
interactive table (e.g., the URLs), but are explicitly listed in the
downloadable {\tt .csv} file.\footnote{The entire dataset provided by
  exoplanets.org is available for download in a single CSV file at
  \url{http://exoplanets.org/csv-files/exoplanets.csv}}

@@

MASS: we use mass-radius relation to get mass.

@@

LAMBDA: the literature has conflicted definitions of LAMBDA, and we
sorted it out and made sure it is consistent in EOD.

I: it used to be for transit systems only. Now sometimes for
non-transiting systems the values of I are also available.

@@

We now report uncertainties for a certain field X as XUPPER, XLOWER
and UX. XUPPER and XLOWER store the upper and lower 1$\sigma$
uncertainties, and they are different when the error bars are
asymmetric. UX contains the 1$\sigma$ uncertainty, and it
equals to $({\rm XUPPER+XLOWER})/2$ in the case of asymmetric error
bars. Fields that have XUPPER, XLOWER and UX are: (list of fields).

@@

Added field: MONTH, PLANETDISCMETH, STARDISCMETH.

@@

VREF is not the same as REF for J H KS, which do not have XREF
fields. See \cite{Wright2011} for references of J H KS mags -- I think
he mentioned it there.

@@

S - changed to SHK; ZZZ What's the source for SHK and RHK? Still discovery
paper and Butler 2006? ZZZ SHK is a poorly maintained field, and it is
unreferenced at the moment though we plan to include propoer reference
in the future.

@@

I\dotfill & Float & Orbital inclination in degrees & -UPPER, etc. \\

@@

SET\dotfill & & Epoch of secondary eclipse center in

@@

MONTH\dotfill & Integer & Month of publication of FIRSTREF & \nodata \\

@@

\tablenotetext{d}{The same as in \cite{Wright2011}, HJD/BJD etc.\ are
  still not consistent.}
